Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Added OpenCL section to the paper.

>>>>

\section{The OpenCL Framework}
For this project, we will use the OpenCL Framework for our kernel lauching.  OpenCL
is an application framework for heterogeneous parallel computing.  It includes an
API for creating and transferring memory to accleration devices, as well as dynamic
compilation of application kernels that are run on the acceleators.Using OpenCL 
allows us to write the host code only once, while allowing us to run the core 
application kernel on the CPU, GPU, or both.

In OpenCL each thread is logically mapped to a work-item.  These work-items are grouped into
workgroups.  These workgroups map to a SM on a discrete GPU.  For instance, these workgroups
share access to a SMs local memory and can perform a barrier with all the other work-items
in the workgroup.  In the case of a CPU acclerator, the workgroups still exist, but optimizations
such as manual caching via local memory will not be effective.

Devices are grouped into contexts, which contains memory buffers and so on.  A queuing system
is used by OpenCL to facilitate kernel execution.  Kernels are submitted to the queue along with
the size of each workgroup, as well as number of workgroups to execute.  This queue is also 
responsible for reading and writing memory buffers.  The queue is in-order, meaning that 
the queue will wait until previously enqueued items have finished before starting work 
on more recently queued items.

For our purposes, we decided to use a seperate context for each device, as well as a seperate
command queue for each context.  We decided to use a seperate context for each device, as it would
allow for finer-grained control of data transfers and residency. Using a seperate command queue
for each device will facilitate multiple devices to be used simultaneously, as each command queue
operates on its own seperate thread.
